---
title: "implyr Example"
author: "Aki Ariga"
date: "3/26/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setting up odbc for macOS

### Install unixODBC with homebrew

```{r, engine='bash', eval=FALSE}
$ brew install unixodbc
```

### Download and install the latest version of the Impala ODBC driver from Cloudera.

You can donwload [the latest Impala ODBC Driver](https://www.cloudera.com/downloads/connectors/impala/odbc.html).

### Configure your .odbc.ini and .odbcinst.ini

After installing Impala ODBC driver for macOS, basic configuration templates can be found in `/opt/cloudera/impalaodbc/Setup/`.

```{r, engine='bash', eval=FALSE}
cp /opt/cloudera/impalaodbc/Setup/odbc.ini ~/.odbc.ini
cp /opt/cloudera/impalaodbc/Setup/odbcinst.ini ~/.odbcinst.ini
```

Before using following setting, you must replace `HOST` and `KrbRealm` with appropriate ones.

```{r, engine='bash', eval=FALSE}
[ODBC]
# Specify any global ODBC configuration here such as ODBC tracing.

[ODBC Data Sources]
Impala=Cloudera ODBC Driver for Impala

[Impala]

# Description: DSN Description.
# This key is not necessary and is only to give a description of the data source.
Description=Cloudera Impala ODBC Driver DSN

# Driver: The location where the ODBC driver is installed to.
Driver=/opt/cloudera/impalaodbc/lib/universal/libclouderaimpalaodbc.dylib

# The DriverUnicodeEncoding setting is only used for SimbaDM
# When set to 1, SimbaDM runs in UTF-16 mode.
# When set to 2, SimbaDM runs in UTF-8 mode.
#DriverUnicodeEncoding=2

# Values for HOST, PORT, KrbFQDN, and KrbServiceName should be set here.
# They can also be specified on the connection string.
HOST=[REPLACE_YOUR_IMPALA_HOST]
PORT=21050
Schema=default

# The authentication mechanism.
# 0 - No authentication (NOSASL)
# 1 - Kerberos authentication (SASL)
# 2 - Username authentication (SASL)
# 3 - Username/password authentication (NOSASL or SASL depending on UseSASL configuration)
AuthMech=1

# Set to 1 to use SASL for authentication. 
# Set to 0 to not use SASL. 
# When using Kerberos authentication (SASL) or Username authentication (SASL) SASL is always used
# and this configuration is ignored. SASL is always not used for No authentication (NOSASL).
UseSASL=1

# Kerberos related settings.
KrbFQDN=_HOST
KrbRealm=[REPLACE_YOUR_REALM]
KrbServiceName=impala

# Username/password authentication with SASL settings.
UID=
PWD=

# Set to 0 to disable SSL.
# Set to 1 to enable SSL.
SSL=1
CAIssuedCertNamesMismatch=1
TrustedCerts=/opt/cloudera/impalaodbc/lib/universal/cacerts.pem

# If you use SSL with AllowSelfSignedServerCert, you can set this configuration.
#AllowSelfSignedServerCert=1

# Specify the proxy user ID to use.
#DelegationUID=

# General settings
TSaslTransportBufSize=1000
RowsFetchedPerBlock=10000
SocketTimeout=0
StringColumnLength=32767
UseNativeQuery=0

```


### Check the configuration

After configuration, you should kinit with your pricipal.

```{r, engine='bash', eval=FALSE}
$ kinit $USER@YOUR_REALM
```

You should replace `$USER` for the appropriate user and `YOUR_REALM` with the appropriate REALM.

Before using RStudio on you mac, you can check configuration with `isql` command.

```{r, engine="bash", eval=FALSE}
$ isql -v "Impala"
+---------------------------------------+
| Connected!                            |
|                                       |
| sql-statement                         |
| help [tablename]                      |
| quit                                  |
|                                       |
+---------------------------------------+
SQL>
```


## Implyr Example

After setting .odbc.ini you can connect secure Impala cluster with {implyr}. For instance, We will visualize [the airports data](http://openflights.org/data.html#airport).

First, install R packages.

```{r install_packages, eval = FALSE}
install.packages(c("implyr", "odbc", "DBI", "dplyr", "ggplot2", "ggExtra"))
```


Then, connect the Impala cluster.

```{r connect_impala}
#Sys.setenv(DYLD_FALLBACK_LIBRARY_PATH="/usr/local/lib")
library(implyr)
library(odbc)
drv <- odbc::odbc()
impala <- src_impala(
  drv = drv,
  dsn = "Impala"
)
```

Show the airports data. In this case, we assume the data is in `u_ariga` database, so that we will change database using `use u_ariga`.

```{r access_flight_data}
library(DBI)
# Change database
dbGetQuery(impala, "use u_ariga")
dbGetQuery(impala, "show tables")
airports <- tbl(impala, "airports_pq")

View(airports)

airports %>% filter(latitude < 35) %>% count()
```

Finally, we will show joint histogram of longitude and latitude.

```{r show_example_histogram}
airports_by_geo <- airports %>% select(longitude, latitude) %>% collect()

library(ggplot2)

p <- ggplot(airports_by_geo, aes(longitude, latitude)) + geom_point() + theme_classic()
ggExtra::ggMarginal(p, type = "histogram")
```